MaxEnt: What is it good for?

### 2015-06-21 ms.tex
Brandeis reminder
special cases of canonical

Throughout this article I will present, but not derive or prove, MaxEnt
results for certain types of testable information. Some of these are well
known (e.g. the expected value constraints discussed in
Section~\ref{sec:expected_values}) while others are less so.

@@

>>>>

Throughout this article I will present, but not derive or prove, MaxEnt
results for certain types of testable information. Some of these are well
known (e.g. the expected value constraints discussed in
Section~\ref{sec:expected_values}, which lead to ``canonical'' probability
distributions which may be familiar from statistical mechanics) while others
are less so. Where possible I will present other results as special cases of
the canonical distribution.

@@

{\bf Brandeis dice problem...MaxEnt solution vs. ``the'' Bayesian solution}
